Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-11 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The Spatio-Temporal Scan statistic was only computed for the number of cumulative cases during the pandemic, the method to calculate spatio-temporal *clusters* showed itself to be way more computer intensive than the calculation of the Global Moran's I and the *Lisa*. But the Spatio-Temporal Scan statistic also was efficient to identify emerging *clusters* in space and time, with most of the locations in October and November also identified in the Local Moran's I for these months.

>>>>

 The Spatio-Temporal Scan statistic was only computed for the number of cumulative cases during the pandemic, the method to calculate spatio-temporal *clusters* showed itself to be way more computer intensive than the calculation of the Global Moran's I and the *LISA*. But the Spatio-Temporal Scan statistic also was efficient to identify emerging *clusters* in space and time, with most of the locations in October and November also identified in the Local Moran's I for these months.
